Response to the defense feedback

### 2021-06-02 response.txt

a. I revised the description in Chapter 5. I avoided the use of term ``lower bound''
and tune my presentation.

b. I revised Table 5.3. The evaluation section does not compare Quincunx with Abacus
in the current version because they are calculated with different methods and have
different threat models.

5. iid assumption – does it fit your research on side-channel?

It is true that Quincunx requires the assumption that input variables are
independent and identically distributed. That's why I applied a blackbox fuzzing 
instead of a coverage-guided fuzzing. As long as each time we get a random input from 
the whole input space (Population) that is independent of the previous input, the input
variables should satisfy the i.i.d. assumption. Take AES-128 encryption for example, 
each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key 
values follows the i.i.d. assumption.

The situation is a little different for a machine learning library. In my
dissertation, we also evaluated Quincunx on a deep learning model. Each time, we
randomly select an item from a dataset (Sample). If the dataset is biased, then we
can not get correct results. The good news is that the most well-known dataset in
machine learning is i.i.d. i.i.d. is the foundation of many machine learning
techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 
simplify many methods by assuming the data won't change over the time. 
In my dissertation, we used MINIST, a well-known handwriting digit dataset. 
We believe the i.i.d. assumption holds under the circumstance, although the
assumption can be violated in some real-world scenarios.

@@

I have revised my dissertation to include the discussion on i.i.d.

6. Some feedback I gave before your defense.

As suggested by Dr. Wu, I added a new chapter on Discussion and Limitations (Chapter 6),
and discussed potential ways and related work to the mitigated reported side
(Chapter 2).

7. Improve English grammar.

Dr. Larus helped me fix a lot of grammar issues. I also revised the dissertation
multiple times. In addition, I used Grammarly to proofread my dissertation.

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.). That's why I apply a black box fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Population) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption. The situation is a little different for machine learning libraries. In the dissertation, we evaluated \ctool{} on a deep learning model. Each time, we randomly select an item from a dataset (Sample). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data set in machine learning is i.i.d.. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. The dataset is widely used in many supervised machine learning tasks.  We believe the i.i.d. assumption holds under the circumstance.

>>>>

\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.). That's why I apply a black box fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Population) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption. The situation is a little different for machine learning libraries. In the dissertation, we evaluated \ctool{} on a deep learning model. Each time, we randomly select an item from a dataset (Sample). If the dataset is biased, then we can not get correct results. The good news is that the most well-known dataset in
machine learning is i.i.d. i.i.d. is the foundation of many machine learning
techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 
simplify many methods by assuming the data won't change over the time. 
In my dissertation, we used MINIST, a well-known handwriting digit dataset. 
We believe the i.i.d. assumption holds under the circumstance, although the
assumption can be violated in some real-world scenarios.
